Working with Math environments in texor

### 2023-07-28 supplement/math-env/math-example.tex
Updated math supplementary material

\begin{align}
f(x) = \frac{1}{\sigma\sqrt{2\pi}} 
  \exp\left( -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{\!2}\,\right)
  \label{eq:2}
\end{align}

\section{Equation Numbering}
\begin{align}
S_{T, s}(z_t) = & X^{\top} K_{b,t}^* X (Z - z_t)^s \nonumber\\
T_{T, s}(z_t) = &X^{\top} K_{b,t}^* Y (Z - z_t)^s,
\label{eq:tvpols}
\end{align}

@@

like instead of \verb|\bm| \verb|\boldmath| use \verb|\mathbb|
avoid custom math commands MathJaX will never be able to parse it

@@

>>>>

Display Math refers to equations, almost all LaTeX equations can be rendered by
MathJax.

\begin{verbatim}
\begin{align}
f(x) = \frac{1}{\sigma\sqrt{2\pi}} 
  \exp\left( -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{\!2}\,\right)
  \label{eq:1}
\end{align}
\end{verbatim}
This will render as \ref{eq:1}.
\begin{align}
f(x) = \frac{1}{\sigma\sqrt{2\pi}} 
  \exp\left( -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{\!2}\,\right)
  \label{eq:1}
\end{align}

\section{Equation Numbering}
In LaTeX your equations get numbered automatically unless you are using \verb|\[..\]| to describe
math. Equation numbering works a bit differently in \CRANpkg{bookdown} (the base of RJ web article format) where
it is mandatory to have a \verb|(\#eq:xx)| which is described in more detail in \citep{bookdown}.

The \CRANpkg{texor} package eases authors from manually adding \verb|(\#eq:xx)| to equations in Rmarkdown
by using pandoc Lua filter to convert existing \verb|\label{..}| in the equations to \verb|(\#eq:xx)|
during conversion. Equation \ref{eq:xe} shows such a use case of equation being numbered by its label in Rmakrdown
as well as LaTeX.

\begin{align}
S_{T, s}(z_t) = & X^{\top} K_{b,t}^* X (Z - z_t)^s 
\label{eq:xe}
\end{align}

Equation labels must start with the prefix \verb|eq:| in bookdown. All labels in bookdown must only contain alphanumeric characters, \verb|:|, \verb|-|, and/or \verb|/| as suggested in \citep{bookdown}.

@@

Altough MathJax does a good job of supporting most LaTeX math functions,
some functions do not work like \verb|\bm| \verb|\boldmath|, instead use \verb|\mathbb|.
Also avoid custom math commands MathJaX will never be able to parse it. The reason being
MathJax renders math case by case and custom commands will already be removed by pandoc
during the conversion, hence MathJax will not be aware of such redefinations.

@@

\bibitem[Yihui (2023)]{bookdown}
Yihui Xie
\newblock bookdown: Authoring Books and Technical Documents with R Markdown
\newblock \penalty0 2023
\newblock URL \url{https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#equations}
